chronos_splines

### 2017-12-26 analysis/chronos/analysis_splines.Rmd
add rwi computations

# Computar los rwi

```{r}
  # rwdf: a ringwidth dataframe. row: years; col: id_cores
# nsmooth: es el tamaño de la wavelength (0.67*long serie; ej.: 30 years)

computeSpline <- function (rwdf, nsmooth){

  rwl_rwi <- c()

  # ID cores 
  cores <- colnames(rwdf)

  for (i in cores) {
    # 1 # Select core
    id_core <- i

    # 1 # Select ring width serie 
    rws <- rwdf[[id_core]]

    # 2 # Prepare data to detrend
    names(rws) <- rownames(rwdf)

    serie_suavizada <- detrend.series(y = rws, method = "Spline",
                                      y.name = id_core, nyrs = nsmooth) 
    serie_suavizada <- as.data.frame(serie_suavizada) 
    colnames(serie_suavizada) <- id_core

    # 4 # Join another detrened series
    rwl_rwi <- cbind(rwl_rwi, serie_suavizada)
  }
  return(rwl_rwi)
}

rwi_sj <- computeSpline(sj, nsmooth = 30)

rwdf <- sj 
cores <- colnames(rwdf)
id_core <- cores[1]

```{r}
source(paste0(di, 'script/R/bai_piovesan.R'))
source(paste0(di, 'script/R/rw_byTree.R'))
source(paste0(di, 'script/R/chrono_bai.R'))
source(paste0(di, 'script/R/suaviza_cronos.R'))
source(paste0(di, 'script/R/correlaBootIC.R'))
```

* Crear dataframes `rwl` por cada sitio CA_High, CA_Low, SJ_High. SJ_Low (:red_circle: mejorar la forma de hacerlo)
    * :red_circle: ojo he cambiado los nombres de las series en SJ y en CA

@@

```{r}
# Create subset to compare between sites 
caL <- ca[,c("CA0101","CA0102","CA0201","CA0202","CA0301","CA0302","CA0401","CA0402","CA0501","CA0502",
             "CA0601","CA0602","CA0701","CA0702","CA0801","CA0802","CA0901","CA0902","CA1001","CA1002",
             "CA2601","CA2602","CA2701","CA2702","CA2801","CA2802","CA2901","CA2902","CA3001","CA3002")] 
caH <- ca[, c("CA1101","CA1102","CA1201","CA1202","CA1301","CA1302","CA1401","CA1402","CA1501","CA1502",
              "CA1601","CA1602","CA1701","CA1702","CA1801","CA1802","CA1901","CA1902","CA2001","CA2002",
              "CA2101","CA2102","CA2201","CA2202","CA2301","CA2302","CA2401","CA2402","CA2501","CA2502")]

sjL <- sj[, c("SJ0101","SJ0102","SJ0201","SJ0202","SJ0301","SJ0302","SJ0401","SJ0402","SJ0501","SJ0502",
              "SJ0601","SJ0602","SJ0603","SJ0701","SJ0702","SJ0801","SJ0802","SJ0901","SJ0902","SJ0903",
              "SJ1001","SJ1002","SJ1003")]
sjH <- sj[, c("SJ1101","SJ1102","SJ1103","SJ1201","SJ1202","SJ1203","SJ1301","SJ1302","SJ1303","SJ1401",
              "SJ1402","SJ1501","SJ1502","SJ1601","SJ1602","SJ1701","SJ1702","SJ1703","SJ1801","SJ1802",
              "SJ1901","SJ1902","SJ2001","SJ2003","SJ2002")]
```

* Lectura y preparación de datos de diámetro

```{r} 
# Prepare Diameter data

# Change name focal according to loc
compete <- compete %>% 
  mutate(id_focalLoc = stringr::str_replace_all(id_focal, c("A" = "SJ", "B" = "CA")))

# Get only focal trees, and only selected variables 
ft <- compete %>% 
  filter(sp=='Focal') %>% 
  filter(id_focal!='Fresno') %>% 
  dplyr::select(id_focal, id_focalLoc, loc, dn_mm, height_cm)

# Set levels of eleveation 
sj_lowcode  <- paste0('SJ', str_pad(1:10, 2, pad='0'))
sj_highcode <- paste0('SJ', 11:20)
ca_lowcode <- c(paste0('CA', str_pad(1:10, 2, pad='0')),
            paste0('CA', 26:30))
ca_highcode <- paste0('CA', 11:25)

ft <- ft %>% 
  mutate(elev = as.factor(
    ifelse(id_focalLoc %in% sj_lowcode, 'Low',
                       ifelse(id_focalLoc %in% sj_highcode, 'High',
                              ifelse(id_focalLoc %in% ca_lowcode, 'Low', 'High'))))) %>%
  mutate(site = as.factor(paste0(loc, '_', elev)))
```

@@

## By site 
```{r}
objects_rwl <- c('caL','caH','sjL','sjH')

>>>>

Computar RWI para tres sitios CA_High, CA_Low, SJ.

# Preparar datos para computar RWI 
```{r}
source(paste0(di, 'script/R/computeSpline.R'))
```

@@

* Crear dataframes `rwl` por cada sitio CA_High, CA_Low, SJ

```{r}
# Create subset to compare between sites 
caL <- ca[,c("CA0101","CA0102","CA0201","CA0202","CA0301","CA0302","CA0401","CA0402","CA0501","CA0502",
             "CA0601","CA0602","CA0701","CA0702","CA0801","CA0802","CA0901","CA0902","CA1001","CA1002",
             "CA2601","CA2602","CA2701","CA2702","CA2801","CA2802","CA2901","CA2902","CA3001","CA3002")] 
caH <- ca[, c("CA1101","CA1102","CA1201","CA1202","CA1301","CA1302","CA1401","CA1402","CA1501","CA1502",
              "CA1601","CA1602","CA1701","CA1702","CA1801","CA1802","CA1901","CA1902","CA2001","CA2002",
              "CA2101","CA2102","CA2201","CA2202","CA2301","CA2302","CA2401","CA2402","CA2501","CA2502")]
```

## Compute RWI

```{r}
rwi_sj <- computeSpline(rwdf = sj, nsmooth = 30)
rwi_caL <- computeSpline(rwdf = caL, nsmooth = 30)
rwi_caH <- computeSpline(rwdf = caH, nsmooth = 30)
```

```{r}

objects_rwi <- c('rwi_caL','rwi_caH','rwi_sj')

for (i in objects_rwi){

  aux <- get(i)

  # Stats of RWI 
  aux_stats <- rwi.stats(aux)

  # Add site 
  aux_stats$site <- as.factor(i)

d <- chron(rwi_sj, biweight = TRUE, prewhiten = TRUE)
dd <- rwi.stats(rwi_sj)

crn.plot(d)

@@

## By site 
```{r}

d <- rwi.stats()

objects_rwl <- c('caL','caH','sjL','sjH')
